Mirror, mirror on the wall. Which's the best match of them all?

### 2024-01-19 PNAS/index.Rnw
dot after e.g. should not be interpreted as the end of a sentence

\firstpage[3]{6}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

\section*{Probability of False Identifications}
There are at least two components of the false positive rate: identifying two pieces of evidence that have similar characteristics but are from different sources (a coincidental match) and procedural failures (e.g. lab process errors) \citep[p 50]{pcast}.
In objective disciplines with standardized evaluation rules (e.g. DNA), these sources can be distinguished.
However, in toolmark examination, no objective evaluation rules are used; examiners testify based on subjective, individual rules for how much similarity is sufficient for an identification.
Assuming that lab procedure errors are not a factor in studies, we use reported error rates from striated evidence comparisons (e.g. excluding breech face comparisons) in open-set studies as an estimate of the coincidental match rate of a single wire-cut comparison.
%% Do we need to address the fact that wire cuts don't have external features to align, where bullets and firing pins do???
The three studies we consider \citep{bajic2020, mattijssen2021,best2022} have false positive rates between 0.0045 \citep{best2022} and 0.072 \citep{mattijssen2021}; pooling data from these studies yields a false positive rate of \Sexpr{sprintf("%.2f", fpr)}.

@@

% References should be cited in numerical order as they appear in text; this will be done automatically via bibtex, e.g. \cite{belkin2002using} and \cite{berard1994embedding,coifman2005geometric,phdthesis,masterthesis}. All references cited in the main text should be included in the main manuscript file.

>>>>

\firstpage[3]{6}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g.\ "\firstpage[4]{11}".

@@

\section*{Probability of False Identifications}
There are at least two components of the false positive rate: identifying two pieces of evidence that have similar characteristics but are from different sources (a coincidental match) and procedural failures (e.g.\ lab process errors) \citep[p 50]{pcast}.
In objective disciplines with standardized evaluation rules (e.g.\ DNA), these sources can be distinguished.
However, in toolmark examination, no objective evaluation rules are used; examiners testify based on subjective, individual rules for how much similarity is sufficient for an identification.
Assuming that lab procedure errors are not a factor in studies, we use reported error rates from striated evidence comparisons (e.g.\ excluding breech face comparisons) in open-set studies as an estimate of the coincidental match rate of a single wire-cut comparison.
%% Do we need to address the fact that wire cuts don't have external features to align, where bullets and firing pins do???
The three studies we consider \citep{bajic2020, mattijssen2021,best2022} have false positive rates between 0.0045 \citep{best2022} and 0.072 \citep{mattijssen2021}; pooling data from these studies yields a false positive rate of \Sexpr{sprintf("%.2f", fpr)}.

@@

% References should be cited in numerical order as they appear in text; this will be done automatically via bibtex, e.g.\ \cite{belkin2002using} and \cite{berard1994embedding,coifman2005geometric,phdthesis,masterthesis}. All references cited in the main text should be included in the main manuscript file.
